---
title: "all features accuracy"
author: "niki"
date: "11 April 2018"
output:
  html_document: default
  pdf_document: default
---



## This case study is to evaluate accuracy when the social network features and node neighbourhood features are used to predict the relation types.As the number of features increases, prediction accuracy rate may increase. we use seed value set to 200 in this case. 
#Archi model: "H:\theis_work\SWC_chair_ml_related\Archi_models\final_airport_backup.archimate"

#Archi template: "H:\theis_work\SWC_chair_ml_related\Archi_templates\version3_template_airport"


#[0]----------------SET STEERING PARAMETERS-----------------------------------------------#placeholders
```{r}
#set the path to access data set
r_fpath = "H:/theis_work/SWC_chair_ml_related/Archi_data/03airport_version3//"
r_f1name = "elements"
r_f2name = "relations"


```


#[1]--------------IMPORT DATASET IN MEMORY FROM DIRECTORY-------------------------------
```{r}
#Upload csv into memory
#Inputparameters:
# - i.fpath: Directory where csv file available
# - i.fname: File name to read/import


read_data <- function(i.fpath, i.fname) { 
  library(readr)
  
  #Bring csv file path and file name together
  fpath <- paste(i.fpath, i.fname, ".csv", sep = "")
  
  #Read csv from path and the given file name
  #Supress warnings because of data from IBM
  df_csv <- suppressWarnings(read_csv(fpath, col_names = TRUE))
  
  return (df_csv)
}
#Store csv in dataframe
elements <- suppressWarnings(read_data(r_fpath, r_f1name))
relations <- suppressWarnings(read_data(r_fpath, r_f2name))

#Retrives the dimension of an object (rows and columns)
dim(elements)
dim(relations)
```

#[2]--------------COMBINE THE DATA FROM MATCHING ELEMENTS AND RELATION DATAFRAME-------------------------------
```{r}
combined_data<- function(df){
  
  new_ele<-elements[match(relations$Source, elements$ID), 3, drop=F]
  new_rel<-elements[match(relations$Target, elements$ID), 3, drop=F]
  
  df<-cbind(new_ele,new_rel)   #new dataframe
  
  #change column names
  colnames(df)[1] <- "new_source"
  colnames(df)[2] <- "new_target"
  
  #combine with the relation2 table
  data<-cbind(relations, df)
  
  
  data$Source<- NULL
  data$Target<- NULL
  return(data)
  
  
}
data<- combined_data(data)
dim(data)
```

#[2]--------------GENERATE GRAPH DATA FROM DATAFRAME-------------------------------

```{r}
#generate Igraph object from dataframe
library(igraph)
g <- graph_from_data_frame(data[, 5:6], directed = TRUE)
g
```

#[3]--------------DATA PREPARATION AND PREPROCESSING-------------------------------
```{r}
#data preparation
no_of_neighbours_source = ego_size(g, order = 1,mode = "out", mindist = 1)
size_neighbours<-data.frame(no_of_neighbours_source)
node<- data.frame(vertex.attributes(g))
df<-cbind(node, size_neighbours)
dat1<-merge(data, df, by.x = "new_source", by.y="name")


#size target neighbours
no_of_neighbours_target = ego_size(g, order = 1,mode = "out", mindist = 1)
size_neighbours<-data.frame(no_of_neighbours_target)
node<- data.frame(vertex.attributes(g))
df<-cbind(node, size_neighbours)
dat2<-merge(dat1, df, by.x = "new_target", by.y="name")

#jaccard similarity
sim<-similarity.jaccard(g, mode = "out")
name<-as.data.frame(vertex.attributes(g))
rownames(sim)<- paste(name$name)
colnames(sim)<- paste(name$name)
jaccard_sim<-as.data.frame(cbind(rep(rownames(sim), ncol(sim)), rep(colnames(sim), 
              each=nrow(sim)), c(sim)))
colnames(jaccard_sim)=c("source","target","Jaccard_simil")
dat3<-merge(dat2, jaccard_sim, by.x = c("new_source", "new_target"), 
              by.y=c("source","target"))

#admir similarity
sim<-similarity.invlogweighted(g, mode = "out")
name<-as.data.frame(vertex.attributes(g))
rownames(sim)<- paste(name$name)
colnames(sim)<- paste(name$name)
admir_sim<-as.data.frame(cbind(rep(rownames(sim), ncol(sim)), rep(colnames(sim), 
              each=nrow(sim)), c(sim)))
colnames(admir_sim)=c("source","target","AdamicAdar_simil")
df_fin<-merge(dat3, admir_sim, by.x = c("new_source", "new_target"), 
              by.y=c("source","target"))

#data preparation
source_degree<- degree(g)
m<-as.data.frame.numeric(source_degree)
m$node<-row.names(m) 
row.names(m) <- NULL
dat1<-merge(df_fin, m, by.x = "new_source", by.y="node")


target_degree<- degree(g)
m<-as.data.frame.numeric(target_degree)
m$node<-row.names(m) 
row.names(m) <- NULL
fin_dat<-merge(dat1, m, by.x = "new_target", by.y="node")

pag<- page.rank(g)
page_source<- pag$vector
m<-as.data.frame.numeric(page_source)
m$node<-row.names(m) 
row.names(m) <- NULL
dats<-merge(fin_dat, m, by.x = "new_source", by.y="node")

page_target<- pag$vector
m<-as.data.frame.numeric(page_target)
m$node<-row.names(m) 
row.names(m) <- NULL
dats2<-merge(dats, m, by.x = "new_target", by.y="node")

source_clus<- transitivity(g, type = "local", isolates = "zero")
clus<- cbind(m, source_clus)
clus$page_target<- NULL
dat_fi<-merge(dats2, clus, by.x = "new_source", by.y="node")


target_clus<- transitivity(g, type = "local", isolates = "zero")
clus<-cbind(m, target_clus)
clus$page_target<- NULL
final<-merge(dat_fi, clus, by.x = "new_target", by.y="node")


source_between<- betweenness(g)
m<-as.data.frame.numeric(source_between)
m$node<-row.names(m) 
row.names(m) <- NULL
df<-merge(final, m, by.x = "new_source", by.y="node")


target_between<- betweenness(g)
m<-as.data.frame.numeric(target_between)
m$node<-row.names(m) 
row.names(m) <- NULL
df_fin<-merge(df, m, by.x = "new_target", by.y="node")


#change df
fin_dat=df_fin



#data prep
fin_dat$Type<- as.factor(as.character(fin_dat$Type))
fin_dat$new_source<- as.factor(as.character(fin_dat$new_source))
fin_dat$new_target<- as.factor(as.character(fin_dat$new_target))
fin_dat$new_source<- as.numeric(as.factor(fin_dat$new_source))
fin_dat$new_target<- as.numeric(as.factor(fin_dat$new_target))
fin_dat$Jaccard_simil<- as.numeric(as.factor(fin_dat$Jaccard_simil))
fin_dat$AdamicAdar_simil<- as.numeric(as.factor(fin_dat$AdamicAdar_simil))

fin_dat$Name<- NULL
fin_dat$Documentation<- NULL


##scale numeric types
##ind <- sapply(fin_dat, is.numeric)
##fin_dat[ind] <- lapply(fin_dat[ind], scale)
```


#[4]--------------DATA PARTITION INTO TRAINING AND TESTING SET-------------------------------

```{r}

library(caret)
#accuracy slightly increased when used jacc similarity and neighbours(outdegree)
set.seed(3033)
intrain <- createDataPartition(y = fin_dat$Type, p= 0.7, list = FALSE)
training <- fin_dat[intrain,]
testing <- fin_dat[-intrain,]

```


##Training models includes by deafault source and target nodes as feature and target class is Type of relationship
##Case study shows how the prediction accuracy changes when the selection of features differs while trining

#[5]--------------TRAIN THE MODEL WITH SOCIAL NETWORK AND NEIGHBOURHOOD FEATURES(ALL FEATURES) WITH UP-SAMPLING METHOD-------------------------------

```{r}
set.seed(200)
trctrl <- trainControl(method = "repeatedcv", number = 10, repeats = 3,sampling = "up")
rf_fit <- train(Type~new_source+new_target+source_degree+target_degree+
                    page_source+page_target+source_clus+target_clus+source_between+
                    target_between+no_of_neighbours_source+no_of_neighbours_target+AdamicAdar_simil, data = training, preProc=c("center","scale"),
                method = "rf",trControl=trctrl,tuneLength = 10 )

#prediction accuracy of unknown dataset(testing)
test_pred <- predict(rf_fit, newdata = testing)

#confusion matrix
confusionMatrix(test_pred, testing$Type)
```




